---
title: "Capstone_Wei Hao"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/vicky/Desktop/Capstone/Yelp Dataset")
library(jsonlite)
business<-stream_in(file("yelp_academic_dataset_business.json"))
business
str(business)

summary(business)
business1<-flatten(business)
View(business1)
str(business1)
library(magrittr)
library(dplyr)
library(tidyr)
business1 %>% mutate(categories= as.character(categories)) %>% select(categories)%>% unnest(categories)
```
```{r}
write.csv(business1,"business.csv")
```


```{r}
#Get rid of variables that we are temporarily not using. 
df<-select(business1, -starts_with("neighborhood"), -starts_with("hours"), -starts_with("attribute"))
df
write.csv(df, "Business.csv")
```

```{r}
#How many businesses in each state and each city?
statebusiness<-as.factor(df$state)
summary(statebusiness)
citybusiness<-as.factor(df$city)
summary(citybusiness)


``````
```{r}
df%>%unnest(categories) %>%
 select(name, categories)%>%group_by(categories)%>%summarise(n=n())%>%arrange(desc(n))%>%head(20)
```


```{r}
#Top Business Categories that are currently open
category<-as.character(df$categories)
topcatogory<-df%>%filter(is_open==1)%>%unnest(categories)%>%select(name, categories)%>%group_by(categories)%>%summarise(n=n())%>%arrange(desc(n))%>%head(30)
topcatogory

#Although there are so many categories with similiar names, we could have a gist of the main categories like restuarant, nail and beauty salons, coffee and tea, auto repair, and bank services. 
write.csv(topcatogory, "TopCat.csv")

```

```{r}
#Restuarants
library(stringr)
library(dplyr)
df%>% filter(str_detect(categories,  "Restaurant"))%>% unnest(categories)%>%filter(categories != "Restaurants")%>% count(categories)%>% 
  arrange(desc(n))
#Top Category in the 10 States
df%>% filter(str_detect(categories,  "Restaurant"))%>% unnest(categories)%>%filter(categories != "Restaurants")%>% count(state, categories)%>% filter(n > 10) %>%
 group_by(state) %>%
 top_n(1, n)%>%
  arrange(desc(n))

```

```{r}

#Beauty Salons

df%>% filter(str_detect(categories,  "Beauty"))%>% unnest(categories)%>%count(categories)%>% 
  arrange(desc(n))
#Top Category in the 10 States
df%>% filter(str_detect(categories,  "Beauty"))%>% unnest(categories)%>% count(state, categories)%>% filter(n > 10) %>%
 group_by(state) %>%
 top_n(1, n)

```

```{r}
df1<-select(business1, -starts_with("neighborhood"), -starts_with("hours"), -starts_with("attribute"), -starts_with("categories"), -starts_with("business_id"), -starts_with("name"),-starts_with("address"), -starts_with("longitude"),-starts_with("latitude"),-starts_with("postal_code"),-starts_with("is_open"))
dfbystatestar<-df1%>%filter(state != '') 
a<-group_by(dfbystatestar, state)
View(dfbystatestar)
View(a)

write.csv(dfbystatestar, "Business_1.csv")

dfbystatestar1<-dfbystatestar%>%summarise(total_businesses=n(), total_reviews=sum(review_count), avg_rating=round(mean(stars),2)) %>% arrange(desc(avg_rating))
View(dfbystatestar1)

write.csv(dfbystatestar1, "Business_2.csv")
```
```{r}
df2<- data.frame(state=business$state, reviews=business$review_count, star=business$stars)
write.csv(df2, "df2.csv")
```

```{r}
setwd("C:/Users/vicky/Desktop/Capstone/Yelp Dataset")
library(jsonlite)
user<-stream_in(file("yelp_academic_dataset_user.json"))
View(user)
str(user)

```

```{r}
user1<-user[-c(5:10, 12:22)]
user1
write.csv(user1, "User.csv")
```

